---
title: "Problem Set #X"
subtitle: "BST 258: Causal Inference -- Theory and Practice"
author: "[Your Name Here]"
date: ""
format:
  pdf:
    documentclass: scrartcl
    papersize: letter
    fontsize: 11pt
    geometry:
      - margin=1in
      - heightrounded
    number-sections: false
    colorlinks: true
    link-citations: true
    callout-appearance: simple
    callout-icon: false
    # figure options
    fig-width: 6
    fig-asp: 0.618
    fig-cap-location: bottom
    # code block options
    code-line-numbers: false
    code-block-bg: false
    highlight-style: gruvbox
bibliography: refs.bib
---

```{r}
#| echo: false
#| message: false
#| label: global-setup
renv::load(here::here())
library(here)
set.seed(11249)
```

\footnotesize
**Problem set policies:** Please provide concise, clear answers for each
question. Note that only writing the result of a calculation without
explanation is not sufficient. For problems involving \textsf{R}, include the
code in your solution, along with any figures or tables.

Please submit your problem set via Canvas in PDF, alongside the corresponding
\textsf{Quarto} (`.qmd`) source file.

We encourage you to discuss problems with other students, but you must
write your final answer in your own words. Solutions prepared "in
committee" are not acceptable. If you do collaborate with classmates on a
problem, please list your collaborators on your solution. Similarly, while you
may find the use of ChatGPT and related tools helpful, disclosing your use of
them is required to adhere to academic/intellectual honesty.
\normalsize


## Question 1

Start answer here

```{r}
#| label: example-q1
library(data.table)
library(tidyverse)
```

{{< pagebreak >}}


## Question 2

Start answer here


{{< pagebreak >}}


## Question 3

Start answer here


{{< pagebreak >}}


## References

::: {#refs}
:::

